|

### 2016-06-24 SAMPLES/FTP/Manual-FTP.Rmd
manuals

1. Make sure [Docker engine](https://docs.docker.com/engine/installation/) is installed and running.
```
docker ps
```
2. Download a sample [p3.config](p3.config) and [MSGFDB_Mods.txt](MSGFDB_Mods.txt) file and put it to a directory. e.g.

```
cd ~/Desktop/PXD001468
```
in this case, ```p3.config``` must have the following fields:
```
REPO = PRIDE
PRIDEID = (e.g: PXD001468) 
RUN_MSGF = (e.g: YES)
METHOD = (e.g: SPECTRUM_COUNT)
```

@@

3. Download / update p3 from Dockerhub, and run the image.

```
docker pull kristiyanto/p3
docker run --rm -v ~/Desktop:/root/data kristiyanto/p3
```
if necessary, another image can be run simultaneously (in a different terminal windows).

4. Once processes completed, the directory will be populated with:
- Mass Spectometry files downloaded from Pride repository (\*.mzid, \*.mzml)
- Peptide Sequence file (\*.fasta)
- MSGF+ output files (\*.mzid, \*.canno, \*.revCat.cnlcp, *.revCat.csarr, \*.revCat.cseq)
- Output table (\*.txt)
- Output file as R objects (\*.rda)

>>>>

1. Make sure [Docker engine](https://docs.docker.com/engine/installation/) is installed and running.
```
docker ps
```
2. Download a sample [p3.config](p3.config) and [MSGFDB_Mods.txt](MSGFDB_Mods.txt) file and put it to a directory. e.g. `~/Desktop/PXD001468`

```
cd ~/Desktop/PXD001468
```
in this case, ```p3.config``` must have the following fields:
```
REPO = FTP
FTP1 = (e.g: ftp://ftp.pride.ebi.ac.uk/pride/data/archive/2015/06/PXD001468) 
RUN_MSGF = (e.g: YES)
METHOD = (e.g: SPECTRUM_COUNT)
```

@@

3. Download / update P3 from Dockerhub, and run the image.

```
eval $(docker-machine env default)
docker pull kristiyanto/p3
docker run --rm -v ~/Desktop/PXD001468:/root/data kristiyanto/p3
```
if necessary, another image can be run simultaneously (in a different terminal windows).
```
docker run --rm -v ~/Desktop/PXD001468:/root/data kristiyanto/p3
```

4. Once processes completed, the directory will be populated with:
+ Mass Spectometry files downloaded from Pride repository (\*.mzid, \*.mzml)
+ MSGF+ output files (\*.mzid, \*.canno, \*.revCat.cnlcp, *.revCat.csarr, \*.revCat.cseq)
+ Output table (\*.txt)
+ Output file as R objects (\*.rda)

***

If the process stop returning error:
* Make sure all the required files are in the folder. E.g: Fasta files sometimes are not provided in the FTP/Pride repository and must be provided manually. 
* Remove all \*.tmp files before re-run the containers.
